Conflict-Free Vertex Coloring Of Planar Graphs

### 2017-02-28 paper/paper.tex
Adding section draft stuff

\maketitle
\begin{abstract}
Abstract goes here...
\end{abstract}

@@

The \emph{conflict-free coloring} problem is a relaxed variation of the vertex coloring problem. The conflict-free coloring problem does not aim to color every vertex such that it is not connected to a vertex of the same color. Rather, it aims to color \emph{enough} vertices such that for every vertex, it is connected to at least one colored vertex.

>>>>

\maketitle
\begin{abstract}
The conflict-free coloring problem is a variation of the vertex coloring problem, a classical NP-hard optimization problem. The conflict-free coloring problem aims to color the vertices of a graph in a way where every vertex is connected to at least one uniquely colored vertex.
\end{abstract}

@@

The \emph{conflict-free coloring} problem is a relaxed variation of the vertex coloring problem. The conflict-free coloring problem does not aim to color every vertex such that it is not connected to a vertex of the same color. Rather, it aims to color \emph{enough} vertices such that for every vertex, it is connected to at least one uniquely colored vertex.
